---
title: "Can human values explain one’s interest in cryptocurrencies? An explorative study in Germany"
author: 
  - name: "Adrian Stanciu"
    affiliation_number: 1
  - name: "Melanie Partsch"
    affiliation_number: 1
  - name: "Mariana Bernardes"
    affiliation_number: 2
  - name: "Ranjit Singh"
    affiliation_number: 1
  - name: "Clemens Lechner"
    affiliation_number: 1
affiliations:
  - "GESIS-Leibniz Institute for the Social Sciences, Mannheim"
  - "University of Bremen, Bremen"
shorttitle: "Values and cryptocurrencies"
authors_note: "For correspondence contact Dr. Adrian Stanciu, Data and Research on Society, GESIS-Leibniz Institute for the Social Sciences, PO Box 12215, 68072 Mannheim, Germany. Email: adrian.stanciu[at]gesis.org"
abstract: "Write abstract here"
keywords: "Values, Cryptocurrencies, Germany"
date: "`r format(Sys.time(), '%d. %B, %Y')`"
doctype: doc
header-includes:
  - \usepackage{subfig}
output: 
  pdf_document:
    template: "style/template.tex"
csl: style/apa.csl
bibliography: reference.bib
---

```{r setup, include=FALSE, results="asis"}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

r <- getOption("repos")
r["CRAN"] <-"https://cloud.r-project.org/"
options(repos=r)

## these are packages needed for these analyses
if (!require(tidyverse)) {
    install.packages("tidyverse")
    require(tidyverse)
}
if (!require(dplyr)) {
    install.packages("dplyr")
    require(dplyr)
}
if (!require(knitr)) {
    install.packages("knitr")
    require(knitr)
}
if (!require(wesanderson)) {
    install.packages("wesanderson")
    require(wesanderson)
}
if (!require(haven)) {
    install.packages("haven")
    require(haven)
}
if (!require(kableExtra)) {
    install.packages("kableExtra")
    require(kableExtra)
}
if (!require(DT)) {
    install.packages("DT")
    require(DT)
}
if (!require(Hmisc)) {
  install.packages("Hmisc")
  require(Hmisc)
}
if (!require(corrplot)) {
  install.packages("corrplot")
  require(corrplot)
}

# 
remotes::install_github("maksimrudnev/LittleHelpers")
# load packages
library("tidyverse")
library("dplyr")
library("knitr")
library("wesanderson")
library("haven")
library("kableExtra")
library("DT")
library("Hmisc")
library("corrplot")

# --- imports data
load("data/df.Rdata")
load("data/descriptives.Rdata")
load("data/pca.Rdata")
load("data/gradient.Rdata")

# --- imports source scripts
source("scripts/helper_functions.R")

# --- theme for plots
mytheme <- theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1, size = 10),
                 panel.background = element_rect(fill="white", color = "grey50"),
                 panel.grid.major.y = element_line(color="grey90"),
                 axis.title.y = element_text(vjust= 0.5, hjust=1, angle = 90) )

```

# Introduction

Cryptocurrencies are digital money, and much more. The idea of cryptocurrency has developed recently, in 2009, when a person or a group of people known as Satoshi Nakamoto have launched a novel currency that was entirely digital and based on a chain of mathematical algorithms. Their vision was one in which the centralized financial system as we know it can one day be de-centralized in that financial transactions will be possible directly between involved parties. The idea was a simple one: by eliminating the role of banks and governmental bodies that secure trust in financial transactions, unnecessary taxes can be eliminated, people can have more control of their finances, as well as global barriers due to currency conversion might as well be abolished. This has since entered the public knowledge domain and is now known as Bitcoin. Several variations of it and a number of alternative cryptocurrencies later, and it is becoming increasingly clear that the topic is no longer in the under-ground of our society, but quite the contrary, it is here to stay.

This research sets to explore reasons why some people are interested in this new form of finance whereas other are against it, or they are skeptical. Throughout the paper we refer to digital currencies and cryptocurrencies interchangebly, despite several differences between them [see @Cryptoverze2020]. We focus on human values as possible explanators and seek to understand associations with engagement with cryptocurrencies in the general German population. We look at the associations between human values in the Theory of Basic Human Values [TBHV, @Schwartz2012] and varying cryptocurrency items as formulated in a recent survey by the OECD [@OECD2019]. Data for the study stems from a quota sample in line with the demographics of the German general population and was collected in April 2022.

## Cryptocurrencies

[input from Mariana]

## Human values

TBHV is currently the most complete theory of human values [@Schwartz2012; @Schwartzetal2012; @SchwartzBoehnke2004]. This theory states that values represent socially desirable goals that individuals pursue in coping with existential needs. There are ten [or nineteen according to the refined theory, @Schwartzetal2012] value types that transcend specific actions and situations and serve as standards (see Figure 1). These value types are universal in the sense that individuals, regardless of age, gender, country of birth or any other attributes, endorse them to some degree. Therefore, people differ not in the endorsement of one value over another, but they do because they prioritize one value more than the other.

![Value typologies specified in the refined TBHV.](img/schwartz_circle.pdf){width="100%"}

The theory organizes value types according to incompatibilities between underlying goal motivation in a circular fashion. For instance, universalism opposes power since the motivational goal of the former is protection for the welfare of all people and of the latter is dominance over people and resources. Or, conformity conflicts with self-direction since the motivational of the former is restraint of impulses likely to violate social expectations or norms and of the latter is independent thought. These examples were not given randomly; due to shared motivational contents, specific values pertain to a higher ordering of values in fact. Self-enhancement, conformity, and tradition all share the goal of maintaining the status quo which is incompatible with the goal of being open to change shared by hedonism, self-transcendence, and self-direction. On the other hand, universalism and benevolence share the goal of transcending the self which contrasts the goal of enhancing the self-shared by achievement and power. It is because of these relations of goal incompatibility that values drive and motivate human behavior [also see @BardiSchwartz2003].

## The present research

Why should it matter if values inform people's interst in cryptocurrencies? What makes values ultimately relevant is that they are culture-informed, have a developmental trajectory that is lifelong [refer here manuscript by Smallenbroek, Stanciu et al], while they can change due to specific life events such as entering parenthood [@Lonnqvistetal2018], but also due to drastic changes in society such as due to the Covid-19 Pandemic [@Danieletal2022]. Cryptocurrencies hold several similarities with other technological advancements such as the Internet and mobile phones. Compared to previous advancements however, the notion of cryptocurrencies is also in a way an economic and a political statement [Mariana = do you have a citation for this?]. Though this technology is still in its onset, there are reasons to expect that it will impact people's financial awareness and potentially people's dependencies on established monetary and governmental institutions [Mariana = do you have a citation for this?].

In other words, the concept of cryptocurrency is potentially going to shape in the future in currently unknown ways people's motivational goals. We speak of the future because we want to raise awareness that a new technology is now being adopted, in spite of groups of people being against it or disbelieving its mission. This is happening. Therefore, to begin understanding how this will shape our beliefs in the future, we reason that the pertinent first step is to explore what makes this technology possible from a social perspective. That is, why some people are interested, engaged with, and open for this form of finance, while others are not.

We study the link between human values and an interest in cryptocurrencies in a general sense. We draw on the Theory of Planned Behavior [TPB, @Ajzen1991; @ConnerArmitage1998] and seek to identify a "gradient" that describes the influence of human values at varying stages in the formation of actual behavior of holding cryptocurrencies. TPB suggests that behavior takes shape after an intention was formed, which in turn has been informed by attitudes, subjective norms and perceived behavioral control. Studying the role of values in the more generalist theory of planned behavior is not a novelty in the literature. For instance, @Kruseetal2019 examined the effects of human values on social entrepreneurship (intention to solving societal issues) as mediated by attitudes, subjective norms and a perceived behavioral control. One further example is the work by @Stanciu2022 on explaining ageism towards older people. Stanciu reasoned that human values can act as internal motives to either suppress or justify negative stereotypes and prejudice which in turn can explain discriminatory behavior towards older people in younger individuals.

[here a paragraph on previous studies on explaning crypto interest. See Marie's document]

Thus, we explore the role of values in (a) creating an intention to (b) presently or in the future hold cryptocurrencies. *Intention creation* is here defined as possessing knowledge of/having awareness of what cryptocurrencies are and what they stand for. *Holding of cryptocurrencies* is here understood as possession/intention on possessing them in the future. Please note that this study does not test for causal mechanisms and therefore the present study frame and hypotheses have the role of guiding our interpretations of findings rather than informing claims about theory. We attempt a first insight into this phenomenon in Germany, while an end-goal is to prepare, so-to-speak, the study of the topic in more generalist surveys here.

We can think of two approaches to how human values contribute to a person's interest in cryptocurrencies. Please note that this is here meant in a general sense; it addresses both awareness and holding of cryptocurrencies as well as overall beliefs about the topic. First, we acknowledge the fact that cryptocurrencies are a new form of finance thus it is potentially linked with people's motivational goals of accepting or rejecting novelty in their life. The first hypothesis is that values of openness to change will associate with a stronger interest in cryptocurrencies (Hypothesis 1).

Second, we acknowledge the primary goal of cryptocurrencies-that of creating a decentralized financial system-thus facilitating financial independence in people who otherwise are dependent on monetary institutions such as banks. We reason that this might be linked with people's motivational goal of self-enhancing themselves, striving for own financial wellbeing that is. The second hypothesis is that values of self-enhancement will associate with a stronger interest in cryptocurrencies (Hypothesis 2).

# Method

## Participants

```{r}
age.m = mean(df_ipst$age) %>% round_df()
age.sd = sd(df_ipst$age) %>% round_df()
age.min = as.numeric(summary(df_ipst$age)[1])
age.max = as.numeric(summary(df_ipst$age)[6])
p.fem = sample[18,5] %>% round_df()
p.emp = sample[8,5] %>% round_df()
p.educ = sample[4,5] %>% round_df()
```

Data from *N* = `r unique(sample$total_n)` participants (age: *M* = `r age.m`, *SD* = `r age.sd`; Min = `r age.min`, Max = `r age.max`) were collected by respondi in April 2022 in Germany. The sampling strategy used predefined quotas of gender, education, and employment in line with the German general population. Of the present sample there were `r p.fem`% women, `r p.emp`% employed, and `r p.educ`% had finished at least ten classes in the local education system (i.e., *Mittlerer Schulabschluss*).

## Measurement

Unless otherwise stated, all measurements were translated from English into German by a bilingual author, and then the German translation was checked by a second bilingual author. Measurement on cryptocurrencies was taken from the OECD report covering the topic in Asia [@OECD2019].

### Values

Human values were measured in the refined TBHV [@Schwartz2012; @Schwartzetal2012] with the available German version of the PVQ-RR instrument [@SchwartzCieciuch2021]. Fifty-seven brief value descriptions of a fictitious character were presented to the study participants. Men and women received their gender specific questionnaire. Study participants were asked to indicate how much they saw themselves similar to these fictitious characters on an asymetric 6-points scale: 1 *not at all like to me*, 2 *not like to me*, 3 *a little like me*, 4 *moderately like me*, 5 *like me*, 6 *very much like me me*. These items were then used to create ten value typologies and 4 higher order values. An example item that measures universalism is: "It is important to him/her that the weak and vulnerable in society be protected."

### Cryptocurrency themes

#### Intention creation

Under intention creation we subsumed awareness and understanding of and general beliefs on cryptocurrencies. *Awareness* was self-reported as (1) *already has* or (2) *never has* heard of them. Awareness served as a filter question: Only participants who already have heard of the topic continued to answer the following questions. The rest were thanked for their participation and their study ended.

*Understanding* was measured with a single-item question as to how good or bad participants understood in their opinion cryptocurrencies. Their answer was recorded on a 5-point Likert scale where 1 = *not that well* and 5 = *very good*.

*General beliefs* were measured in five questions, each probing a distinct dimension of concern (or hope) among people in society: Cryptocurrencies (1) are an investment opportunity, (2) can be a money exchange opportunity, (3) are regularized by the state and (4) facilitate illegal commerce. The fifth item asked whether participants thought that it was a good time to buy cryptocurrencies. These items were measured on a 5-point Likert scale where 1 = *complete disagreement* and 5 = *complete agreement*.

The latter two questions were shown only to those participants who already heard of cryptocurrencies.

#### Holding

Under *holding* we subsumed presently holding or in the future intending on holding cryptocurrencies as well as reasons for doing so. Answer options for holding behavior were (1) *now*, (2) *in the past*, or (3) *never*. This question was a filter question to reasons for acquisition: Participants who chose either of the first two answer options were later inquired about their reasons for holding cryptocurrencies, whereas participants who chose the latter answer option were inquired about their reasons for not holding cryptocurrencies.

*Holding in the future* was measured with a single-item while the answer options were (1) *would like to*, (2) *would not like to*, or (3) *undecided*.

*Reasons for acquiring cryptocurrencies* were measured with a single-item and participants could choose up to three of eleven answers: (1) fear of missing out, (2) for fun, (3) to learn more about cryptocurrencies, (4) win money fast, (5) long-term investment option, (6) inheritance purposes, (7) support of Block-chain technology, (8) online shopping, (9) money transfer, (10) investment portofolio diversification, (11) other reason.

*Reasons for not acquiring cryptocurrencies* were measured with a single-item question and participants could choose up to three of ten answers: (1) cannot afford it, (2) risk is too high, (3) insufficient knowledge, (4) insufficient control by state, (5) other investment more appealing, (6) no interest in cryptocurrencies, (7) generally no interest in investment, (8) price volatility is worrying, (9) money needed for other things, (10) other reason.

## Aanalytical approach

We studied the link between human values and interest in cryptocurrencies in an explorative manner. First, we looked for evidence on limitations of the present sample concerning its representativity to the German general population. To do so, we compared the sample quotas of gender, age and education to the respective population numbers from the German Microcensus, which covers 1% of the persons and households [\@ add literature]. Furthermore, we used secondary resources such as published literature [e.g., @Witteetal2020] and available data sets [European Social Survey, \@ add literature] to understand how did the present sample fare when compared to the German general population in view of percentage of people with a specific value preference.

Second, we decomposed the present sample according to a gradient from intention creation to behavior. Since the present data was collected with a questionnaire that used strategic filter questions, we were able to re-trace at the sample level which participants (1) heard of, (2) currently are and (3) intend on holding cryptocurrencies. This funneling out due to study design allowed us then to explore at each stage the role of human values. That is, we investigated frequency distributions, density curves, and central tendency indicators (e.g., mean, median) and determined whether human values had comparable roles at each of the three levels mentioned above.

Finally, we explored associations between human values and beliefs that people associated with the cryptocurrency topic, as well as reasons for either holding or not holding cryptocurrencies.

[use beliefs as moderators to the paths values - holding behavior?]

# Results

## Sample representativity

## Gradient from intention to behavior

## Associations

## Descriptives

```{r}
# alternative to the one below
gradient_descriptive %>% knitr::kable(caption="Gradient interest in cryptocurrencies in the present sample",
                                      format="pipe", digits = 2) 
```

# Discussion

Our sample was not representative to the German general population, but it used strict quotas of gender, age and education. Please note that our intention was to gain first insights into an overall pattern regarding adoption of cryptocurrencies in society.

## Limitations and future research

# Conclusion

# References
