---
title: "Can human values explain one’s interest in cryptocurrencies? A correlational study in Germany"
author: 
  - name: "Adrian Stanciu"
    affiliation_number: 1
  - name: "Melanie Partsch"
    affiliation_number: 1
  - name: "Mariana Bernardes da Silva Passos"
    affiliation_number: 2
  - name: "Ranjit Singh"
    affiliation_numer: 1
  - name: "Clemens Lechner"
    affiliation_number: 1
affiliations: 
  - "Data and Research on Society, GESIS-Leibniz Institute for the Social Sciences, Mannheim"
  - "University of Bremen, Bremen"
shorttitle: "Values and cryptocurrencies"
authors_note: "For correspondence contact Dr. Adrian Stanciu, Data and Research on Society, GESIS-Leibniz Institute for the Social Sciences, PO Box 12215, 68072 Mannheim, Germany. Email: adrian.stanciu[at]gesis.org"
abstract: "Write abstract here"
keywords: "Values, Cryptocurrencies, Germany"
date: "`r format(Sys.time(), '%d. %B, %Y')`"
doctype: doc
header-includes:
  - \usepackage{subfig}
output: 
  pdf_document:
    template: "style/template.tex"
csl: style/apa.csl
#bibliography: reference.bib
---


```{r setup, include=FALSE, results="asis"}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

r <- getOption("repos")
r["CRAN"] <-"https://cloud.r-project.org/"
options(repos=r)

## these are packages needed for these analyses
if (!require(tidyverse)) {
    install.packages("tidyverse")
    require(tidyverse)
}
if (!require(dplyr)) {
    install.packages("dplyr")
    require(dplyr)
}
if (!require(knitr)) {
    install.packages("knitr")
    require(knitr)
}
if (!require(wesanderson)) {
    install.packages("wesanderson")
    require(wesanderson)
}
if (!require(haven)) {
    install.packages("haven")
    require(haven)
}
if (!require(kableExtra)) {
    install.packages("kableExtra")
    require(kableExtra)
}
if (!require(DT)) {
    install.packages("DT")
    require(DT)
}
if (!require(Hmisc)) {
  install.packages("Hmisc")
  require(Hmisc)
}
if (!require(corrplot)) {
  install.packages("corrplot")
  require(corrplot)
}

# load packages
library("tidyverse")
library("dplyr")
library("knitr")
library("wesanderson")
library("haven")
library("kableExtra")
library("DT")
library("Hmisc")
library("corrplot")

# --- imports data
load("data/df.Rdata")
load("data/descriptives.Rdata")
load("data/pca.Rdata")

# --- imports source scripts
source("scripts/helper_functions.R")

# --- theme for plots
mytheme <- theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1, size = 10),
                 panel.background = element_rect(fill="white", color = "grey50"),
                 panel.grid.major.y = element_line(color="grey90"),
                 axis.title.y = element_text(vjust= 0.5, hjust=1, angle = 90) )

```

___
# Preamble

Cryptocurrencies are digital money, and much more. The idea of cryptocurrency has developed only recently, in 2009, when a person or a group of people known as Satoshi Nakamoto have launched a novel currency that was entirely digital and based on a chain of mathematical algorithms. Their vision was one in which the centralized financial system as we know it can one day be de-centralized in that financial transactions will be possible directly between involved parties. The idea was a simple one: by eliminating the role of banks and governmental bodies that secure trust in financial transactions, unnecessary taxes can be eliminated, people can have more control of their finances, as well as global barriers due to currency conversion might as well be abolished. This has since entered the public knowledge domain and is now known as Bitcoin. Several variations of it and a number of alternative cryptocurrencies later, and it is becoming increasingly clear that the topic is no longer in the under-ground of our society, but quite the contrary, it slowly grows into yet another domain where there is divide between individuals. 

This research sets to explore reasons why some people are interested in this new form of finance whereas other are against it, or they are skeptical. We focus on the role of human values as possible explanators and seek to understand associations with an interest and motivation to invest in cryptocurrencies among the general German population.

We look at the associations between the ten values and the four higher order orientations postulated in the Schwartz theory and varying cryptocurrency items.

TO DO LIST:

- table with constructs and items (pvq dimensions; crypto-items)
- which constructs/items can be treated as continuous, which must be treated as ordinal

# Hypotheses

This study explores the present topic and it does not test for causal mechanisms. As such, the present hypotheses have the role of  guiding our interpretations of findings, rather than informing claims about theory. 

We can think of two approaches to how human values contribute to a person's interest in crypto-currencies. Please note that interest in crypto-currencies is here meant in a general sense which addresses both awareness, currency-holding, as well as overall beliefs about the topic.

First, we acknowledge the fact that crypto-currencies are a new form of finance thus it is potentially linked with people's motivational goals of accepting or rejecting novelty in their life. The hypothesis is that values of openness to change will associate with a stronger interest in crypto-currencies. 

Second, we acknowledge the primary goal of crypto-currencies - that of creating a decentralized financial system - thus facilitating financial independence in people who otherwise are dependent on monetary institutions such as banks. We reason that this might be linked with people's motivational goal of self-enhancing themselves, striving for own financial well-being that is. The hypothesis is that values of self-enhancement will associate with a stronger interest in crypto-currencies.

Whay should it matter if values inform people's interst in cryptocurrencies? Values are beliefs that guide action in people, and this holds across cultures and contexts. What makes values ultimately relevant is that they are culture-informed, have a developmental trajectory that is lifelong, while they they can change due to life events such as entering parenthood, but also due to drastic changes in society such as due to the Covid-19 Pandemic. 

Cryptocurrencies hold several similarities with previous recent technological advancements in society such as the onset of the internet and of mobile phones. But, compared to previous advancements the notion of cryptocurrencies is also in a way an economic and political statement. Since this technology is still in its onset phase, but has already shown signs of becoming an established part of our society, there are reasons to expect that it will impact people's financial independence and potentially people's dependencies on established monetary and governmental institutions. 

In other words, the concept of cryptocurrency is potentially going to shape in the future in currently unknown ways people's motivational goals. We speak of the future because we want to raise awareness that a new technology is now being adopted, in spite of groups of people being against it or disbelieving its mission. This is happening. Therefore, to begin understanding how this will shape our beliefs in the future, we reason that the pertinent first step is to explore what makes this technology possible from a social perspective. That is, why some people are interested, engaged, and open for this form of finance, while others are not. 

___
# Data prepartion

## Participants

Overall there are **N = `r unique(sample$total_n)`** participants who have at least heard of crypto-currencies. This is our sample for the study.

```{r}
sample %>% 
  kableExtra::kable(caption="Sample description", 
                    digits = 2) %>% 
  kable_styling()
```

## Correlations 

```{r,include=FALSE,echo=FALSE}
correlations_pvq <- correlations %>% 
  filter(var1 %in% c("pvq_SEN",
                    "pvq_CON",
                    "pvq_STR",
                    "pvq_OCH")) %>% 
 filter(grepl("kryftl",var2)) %>% 
   round_df() %>%
  DT::datatable(caption="Correlations between PVQ HOV and Financial and technological literacy")

correlations_pvq
```

```{r,echo=FALSE}
corr_v3 %>% 
  round_df() %>% 
  DT::datatable(caption="Correlation coefficients")
```

___
# Descriptives

## Scale reliabilities

```{r}
cronbach %>% DT::datatable(caption="Scale reliabilities alpha for PVQ-12 and PVQ-HOV")
```

# PCA: Financial and techonological literacy items

Financial and technological literacy of participant was measured with 7 items as used in the OECD Consumer Insights Survey on Cryptoassets ([see here](https://www.oecd.org/financial/education/consumer-insights-survey-on-cryptoassets.pdf)). 


```{r}
labels_literacy %>% select(var_name,variable_label) %>% 
  knitr::kable(caption="List of items measuring financial and technological literacy.") %>% 
  kable_styling()
```

## Loadings

A Principal Component Analysis is conducted on the items measuring financial and technological literacy. 

```{r}
pca[["loadings"]] %>% 
  as.matrix.data.frame(rownames.force = TRUE) %>% 
  as_tibble(rownames = "item") %>% 
  ggplot(., aes(x = V1, y = V2)) +  
  geom_text(aes(x = V1, y = V2, 
                label = item), nudge_x = 0.075) +
  geom_point() +
  labs(title = "Item loadings on 2 extracted factors") +
  mytheme
```

Structure. 

```{r}
pca$loadings[1:7,] %>% knitr::kable(caption="Factor loadings for financial and technological literacy", 
                                    digits = 3) %>% 
  kable_styling()
```


These plots depict the role of the 2 PC in explaining the variation in answers as per grouping variables. 

### Gender

```{r}
pca_sex
```

### Education

```{r}
pca_edu
```

### Holds cryptocurrencies

```{r}
pca_cryptohold
```

### Holds cryptocurrencies in the future

```{r}
pca_cryptoholdfutur
```


Accordingly, two factors are construed:

- **Dim1="financial opportunism"** = `kryftl01,kryftl05,kryftl06`
- **Dim2="financial satisfaction"** = `kryftl02, kryftl07`

Scale reliabilities are presented here. 

```{r}
cronb_lit %>% knitr::kable(caption="Cronbach alpha for financial satisfaction and opportunism",
                           digits = 3) %>% 
  kable_styling()
```

___
To do list:

- set na == DONE
- combine male and female pvq versions into one item == DONE
- check for reverse coding == DONE
- identify which items belong to which constructs: especially for valigo, pvq == DONE
- create the new twelve Schwartz value orientations == DONE
- calculate scale reliability for the new twelve Schwartz value orientations for pvq == DONE
- calculate scale reliability == DONE for HOV
- construct ipsatized indices for valigo and/pvq == DONE
- PCA on financial and technological literacy == DONE
- calculate scale reliability for constructs from the PCA on literacy items 
- construct scales for constructs from the PCA on literacy items 

